
JAVA INTERVIEW QUESTIONS (BIG LIST – NO REPEATS)**

---
 **Java Basics**

1. What is Java? Explain its features.
2. Why is Java platform-independent?
3. What is bytecode?
4. What is JVM? Is JVM platform-dependent? Why?
5. What is JDK, JRE, JVM? Differences?
6. Why is Java called a “robust” language?
7. What is WORA in Java?
8. What is the difference between JDK 8 vs latest JDK? (Common question)
9. What is the difference between compiler and interpreter?
10. What are tokens in Java?

---

 **Data Types & Variables**

11. What are primitive data types in Java?
12. What are non-primitive data types?
13. What is the default value of each datatype?
14. What are variables?
15. What are the types of variables? (Local, Instance, Static)
16. What is the difference between instance and static variables?
17. Why is String a non-primitive type?

---
 **Operators & Type Casting**

18. What is type casting?
19. What is widening and narrowing?
20. Can narrowing cause data loss?
21. Is widening implicit or explicit?
22. What is the difference between == and = ?
23. What is the difference between == and .equals() ?
24. Can we compare two Strings using ==?
25. What are arithmetic, logical, relational operators?
26. What is a ternary operator?

---
 **Control Statements**

27. What is the difference between if and switch?
28. Why can't we use float/double in switch?
29. What is fall-through in switch?
30. What is the difference between break and continue?
31. Where can we use return keyword?
32. What is an infinite loop?
33. Difference between while and do-while loop?
34. Can we use break without a loop or switch?

---
 **OOPs Concepts**

35. What is object?
36. What is class?
37. What is OOP?
38. What are the 4 pillars of OOP?
39. What is encapsulation?
40. What is inheritance?
41. What is polymorphism?
42. What is abstraction?
43. What is method overloading?
44. Why method overloading is compile-time polymorphism?
45. Can we overload main() method?
46. What is method overriding?
47. Why overriding is runtime polymorphism?
48. Difference between overloading and overriding?
49. Can static methods be overridden?
50. Can constructors be overridden?
51. What is super keyword?
52. What is this keyword?
53. Can constructor call another constructor? (Yes → this())
54. Can constructor call parent constructor? (Yes → super())
55. Why constructors don’t have return type?

---
 **Inheritance**

56. What are the types of inheritance?
57. Why multiple inheritance is not supported in Java (classes)?
58. What is hierarchical inheritance?
59. What is hybrid inheritance?
60. Does Java support hybrid inheritance?
61. Can an abstract class have a constructor?

---
 **Abstraction, Interface**

62. What is an abstract class?
63. What is an interface?
64. Differences between abstract class and interface?
65. Can an interface have static methods?
66. Can an interface have default methods?
67. Can we create an object of an interface?
68. Can abstract methods be private?
69. Can an interface extend multiple interfaces?
70. Can an interface extend a class?

---
 **String & StringBuffer**

71. Why is String immutable?
72. What is the difference between String, StringBuilder, StringBuffer?
73. What is a String pool?
74. What is intern() method?
75. Why is StringBuffer thread-safe?
76. Why StringBuilder is faster than StringBuffer?
77. Does “+” operator create new String objects?

---
 **Arrays**

78. What is an array?
79. What are the disadvantages of arrays?
80. Difference between single-dimensional and multi-dimensional array?
81. Can arrays be resized?
82. What happens when accessing array index out of range?

---
 **Exception Handling**

83. What is an exception?
84. What is the difference between error and exception?
85. Types of exceptions? (checked/unchecked)
86. Difference between throw and throws?
87. What is finally block?
88. Can finally block be skipped?
89. What is try-with-resources?
90. What is custom exception?

---
 **Keywords**

91. What is final keyword?
92. final variable vs final method vs final class?
93. What is static keyword?
94. What are static blocks?
95. What is synchronized keyword?
96. What is volatile keyword?
97. What is transient keyword?
98. What is instanceof operator?

---
 **Memory & Garbage Collection**

99. What is heap and stack memory?
100. What is garbage collector?
101. How does garbage collection work?
102. What is finalize() method?
103. Difference between strong, weak, and soft references?

---
 **Packages**

104. What is a package?
105. Types of packages?
106. What is import statement used for?
107. What is fully qualified class name?

---
 **Collections (Basic Questions Only)**

108. What is Collection Framework?
109. Difference between List, Set, Map?
110. Difference between ArrayList and LinkedList?
111. Difference between HashMap and Hashtable?
112. Difference between HashSet and TreeSet?
113. What is iterator?
114. What is fail-fast and fail-safe?
115. What is comparable vs comparator?

---
 **Multithreading (Basic)**

116. What is a thread?
117. How to create a thread?
118. Difference between run() and start()?
119. What is thread lifecycle?
120. What is synchronization?
121. What is deadlock?
122. Difference between process and thread?
123. What is thread priority?

---
 **Miscellaneous**

124. Difference between path and classpath?
125. Why main method is static?
126. What happens if we remove static from main method?
127. Can we compile without main method?
128. Can we run a program without main method?
129. What does System.out.println() internally do?
130. What is wrapper class?
131. Why autoboxing and unboxing are needed?
132. What is === in Java? (Trick question – doesn’t exist)
133. Can a class have multiple public classes?
134. What is recursion?
135. Does Java support pointers?
136. What is immutability?


---

 **EASY LEVEL (Perfect for Warm-up)**

### **Number Programs**

1. Print even and odd numbers in a range.
2. Find whether a number is prime or not.
3. Reverse a number.
4. Check whether a number is palindrome.
5. Find the factorial of a number.
6. Check if a number is Armstrong or not.
7. Sum of digits of a number.
8. Count digits in a number.
9. Print Fibonacci series up to N terms.
10. Find greatest of three numbers.
11. Swap two numbers without using third variable.
12. Find LCM and HCF (GCD) of two numbers.
13. Check if a number is perfect number.
14. Count number of vowels and consonants (from input).
15. Print multiplication table of a number.

---

 **EASY-MEDIUM LEVEL**

### **Arrays**

16. Find largest element in an array.
17. Find smallest element in an array.
18. Reverse an array.
19. Check if array is sorted or not.
20. Find second largest number in array.
21. Remove duplicate elements from array.
22. Count frequency of each element in array.
23. Left rotation of an array.
24. Right rotation of an array.
25. Merge two arrays.
26. Find missing number in an array (1 to n).
27. Find duplicate number in array.
28. Move all zeroes to end of array.
29. Find sum of array elements.
30. Print elements at even/odd positions in array.

---

 **Strings**

31. Reverse a string without using built-in methods.
32. Check if string is palindrome.
33. Count vowels, consonants, digits, and spaces.
34. Remove all white spaces from string.
35. Find duplicate characters in string.
36. Find frequency of characters.
37. Convert lowercase to uppercase without using function.
38. Replace given character in a string.
39. Check anagram of two strings.
40. Remove special characters from a string.
41. Find longest word in a sentence.

---

 **MEDIUM LEVEL**

### **Patterns**

42. Print star pyramid.
43. Print inverted pyramid.
44. Print number pyramid.
45. Print Floyd’s triangle.
46. Print Pascal’s triangle.
47. Print diamond pattern.

---

### **Object-Oriented Coding**

48. Create a Student class with rollno, name, marks → print top scorer.
49. Create Employee class → calculate salary with bonus.
50. Create BankAccount class → deposit, withdraw, check balance.
51. Create Calculator class → method overloading for add().
52. Demonstrate constructor overloading.
53. Demonstrate method overriding using Animal → Dog example.

---

### **Searching & Sorting**

54. Implement linear search.
55. Implement binary search.
56. Implement bubble sort.
57. Implement selection sort.
58. Implement insertion sort.
59. Find Kth largest element in array.

---

### **Math-Based**

60. Find all prime numbers between two intervals.
61. Count prime numbers in array.
62. Convert decimal to binary.
63. Convert binary to decimal.
64. Print Armstrong numbers between 1–1000.

---

 **MEDIUM-HARD LEVEL**

### **Advanced Arrays**

65. Find maximum subarray sum (Kadane’s Algorithm).
66. Find pair of elements whose sum is equal to target.
67. Find all pairs with given sum.
68. Count number of even and odd elements.
69. Sort array in descending order.
70. Find first non-repeating element in array.
71. Find common elements in two arrays.
72. Separate even and odd numbers in array.
73. Reverse each word in a sentence.
74. Merge two sorted arrays.

---

### **Matrix Problems**

75. Print matrix in spiral form.
76. Find transpose of matrix.
77. Addition of two matrices.
78. Multiply two matrices.
79. Check if matrix is symmetric.
80. Count zeroes in matrix.
81. Find sum of diagonal elements.

---

### **Recursion**

82. Find factorial using recursion.
83. Fibonacci using recursion.
84. Power of number using recursion.
85. Sum of natural numbers using recursion.
86. Find GCD using recursion.
87. Reverse a string using recursion.

---

 **HARD LEVEL**

### **String Algorithms**

88. Find longest substring without repeating characters.
89. Find first non-repeating character in string.
90. Implement your own `indexOf()` method.
91. Find occurrences of a substring inside a string.
92. Check if string contains only digits.
93. Count occurrences of each word in a paragraph.

---

### **Complex Logic**

94. Implement custom stack using array.
95. Implement custom queue using array.
96. Implement dynamic array (ArrayList-like).
97. Find majority element (appears more than n/2 times).
98. Check balanced parentheses using stack.
99. Find maximum occurring character in string.
100. Implement custom LinkedList with insert/delete.
101. Reverse a LinkedList.
102. Detect cycle in a LinkedList.

---

### **Threading**

103. Create a thread using Thread class.
104. Create a thread using Runnable interface.
105. Print numbers alternately using two threads.

---

### **Tricky Logic**

106. Without using loop print numbers 1–100.
107. Swap two strings without using third variable.
108. Print repeated elements in array without using extra space.
109. Shuffle array elements randomly.
110. Generate OTP of 6 digits.


