Basic SQL

What is SQL?

What are the different types of SQL commands?

What is the difference between DDL, DML, DCL, and TCL?

What is the difference between CHAR and VARCHAR?

What is the difference between DELETE and TRUNCATE?

What is a PRIMARY KEY and a FOREIGN KEY?

What is a UNIQUE constraint?

What is the difference between NULL and NOT NULL?

What is a DEFAULT constraint?

What is a CHECK constraint?

What is a VIEW and why is it used?

What is an INDEX?

Intermediate SQL

What is the difference between INNER JOIN and LEFT JOIN?

What is the difference between RIGHT JOIN and FULL OUTER JOIN?

What is a SELF JOIN? Give an example.

What is the difference between WHERE and HAVING clause?

What is GROUP BY and why do we use it?

What is ORDER BY?

What is the difference between COUNT(*) and COUNT(column_name)?

What is the difference between UNION and UNION ALL?

What is a CROSS JOIN?

What are aggregate functions? Give examples (SUM, AVG, MIN, MAX, COUNT).

What are scalar functions? Give examples (LEN, ROUND, NOW).

What is the difference between TRIGGER and STORED PROCEDURE?

What is the difference between RANK(), DENSE_RANK(), and ROW_NUMBER()?

Advanced SQL

What is a CLUSTERED INDEX vs NON-CLUSTERED INDEX?

What are transactions and what is ACID property?

What is the difference between COMMIT, ROLLBACK, and SAVEPOINT?

What is a CTE (Common Table Expression)? Give an example.

What is a subquery and a correlated subquery?

What are temporary tables?

What is partitioning in SQL?

What is the difference between DELETE, TRUNCATE, and DROP?

How do you handle duplicate records in a table?

How do you optimize a slow SQL query?

Scenario / Practical SQL Questions

Write a query to find second highest salary in Employee table.

Write a query to find duplicate records in a table.

Write a query to count employees in each department.

Write a query to get employees who joined in the last 30 days.

Write a query to concatenate first name and last name of employees.

Write a query to update multiple rows conditionally.

Write a query to delete duplicate rows but keep one.

Write a query to find employees with no department assigned.

Write a query to get top 5 salaries from Employee table.

Write a query to find department with maximum employees.

Optional / Advanced Concepts

What is a materialized view?

What is index fragmentation?

What is database normalization and denormalization?

What is dynamic SQL?

What is window function and how is it different from aggregate function?